---
title: "Name: yujin pan"
author: Yujin Pan
- |
    | Student number: 22208668
date: "`r format(Sys.time(), '%X, %d %B, %Y')`"
output: html_document
---
# Originality declaration  

I, Yujin Pan, confirm that the work presented in this assessment is my own. Where information has been derived from other sources, I confirm that this has been indicated in the work.

date: `r format(Sys.time(), '%d %B, %Y')`

# Start your response here

## Initial project scope

WRITE A PROJECT SCOPE (we will cover this in the next few weeks in more detail)

* What is my research question - is it different to the set question and why

* Is it appropriate to use 2020 as a year? 

>  This research will identify spatial patterns that can be used to inform future work on spatial factors on New York evicitions

> My question is "are the evicitions in 2020 for New York spatially random or do they exhibit clustering"

> A question for Spatial autocorrelation..."are the densitites of evicitions in New York similar over commnity districts from 2020 to 2022" 

The null hypothesis that I am going to test empirically is that there is no relationship 
  * with points  
  * densities of community districts 
  * with other factors that across New York

* Data
  * What do i have
  The data about New York community districts and the list of evictions.
  * What does it contain
  
  * What are the NA values - do they matter
  
  * Who collected the data - will they have any bias (e.g. remember gerrymandering / using data for a )
  
  * Is there any accuracy information associated with the data - probably not
  
  * What is the CRS - is that useful
  
  * Do i need anything else or what might be useful 
  
* How will i wrangle the data (based on the previous points) to apply the methods

* What are the limitations and assumptions (of either the data or the analysis)

This is an essential part of your submission and worth 20%. In the past students have just written a line and failed this criterion (you don't have to pass each criterion).
```{r}
library(here)
library(janitor)
library(sf)
library(tidyverse)
library(tmap)
library(spatstat)
```

read and filter the data
```{r}
yorkborough <- st_read(here::here("Community Districts","geo_export_e8f41164-4df3-47a2-a939-ca8bcc14f254.shp"))
EvictionData <- read_csv("Evictions.csv",na = "") %>% 
  clean_names()
```
```{r}

??st_geometry
```{r}
Datatypelist <- EvictionData %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")
Datatypelist
```
there are some missing data in longitude and latitude and i need to filter the data....delete the missing data 
convert csv to sf and make crs same
```{r}
PointsData <- EvictionData %>%
  filter(longitude<0 & latitude>0) %>%
  st_as_sf(., coords = c("longitude", "latitude"), 
                   crs = 4326)
yorkborough <- yorkborough %>%
  st_transform(.,4326)
```

make a map and view whether the points is outside the borough
```{r}
tmap_mode("plot")
tm_shape(yorkborough) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(PointsData) +
  tm_dots(col = "red")
```
 But there are many points and i need to check them through a spatial subset
```{r}
PointsData_sub <- PointsData[yorkborough,]
  
```
and the data shows the points is all inside the borough

data analysis
假如是筛选三年的数据 用或者来表示：
EvictionData <- EvictionData %>%
  filter(str_detect(executed_date,"2020$|2021$|2022$"))
```{r}
points_sub2020 <- PointsData_sub %>%
  filter(str_detect(executed_date,"2020|2021|2022"))%>%
  filter(eviction_legal_possession=="Eviction")%>%
  filter(residential_commercial=="Residential")
```
make a map
```{r}
tmap_mode("plot")
tm_shape(yorkborough) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(points_sub2020) +
  tm_dots(col = "red")
```
```{r}
yorhborough_projected <- yorkborough%>%
  st_transform(., 6538)

points_sub2020_projected <- points_sub2020 %>%
  st_transform(., 6538)
window <- as.owin(yorhborough_projected)
plot(window)
```


```{r}
#create a sp object
points_sub2020_projected_sp<- points_sub2020_projected %>%
  as(., 'Spatial')
#create a ppp object
points_sub2020_projected_sp.ppp <- ppp(x=points_sub2020_projected_sp@coords[,1],
                          y=points_sub2020_projected_sp@coords[,2],
                          window=window)
```
```{r}
K <- points_sub2020_projected_sp.ppp %>%
  Kest(., correction="border") %>%
  plot()
```

use DBSCAN
```{r}
library(sp)

#first extract the points from the spatial points data frame
points_todf <- points_sub2020_projected_sp %>%
  coordinates(.)%>%
  as.data.frame()
```
```{r}
points_todf_DBSCAN <- points_todf %>%
  fpc::dbscan(.,eps = 3000, MinPts = 7)
points_todf%>%
  dbscan::kNNdistplot(.,k=7)
?dbscan::kNNdistplot
#plot the data
plot(points_todf_DBSCAN, points_todf, main = "DBSCAN Output", frame = F)
plot(yorhborough_projected$geometry, add=T)
```
Add the cluster information to our original dataframe
```{r}
points_todf<- points_todf %>%
  mutate(dbcluster=points_todf_DBSCAN$cluster)
```
```{r}
tosf <- points_todf%>%
  st_as_sf(., coords = c("coords.x1", "coords.x2"), 
                   crs = 6538)%>%
  filter(dbcluster>0)
```

```{r}
ggplot(data = yorhborough_projected) +
  # add the geometry of the community areas
  geom_sf() +
  # add the geometry of the points - i have had to set the data here to add the layer
  geom_sf(data = tosf, size = 0.4, colour=tosf$dbcluster, fill=tosf$dbcluster)
```
```{r}
library(tmap)
library(sf)

#tmaptools::palette_explorer()
library(RColorBrewer)
library(tmaptools)
colours<- get_brewer_pal("Set1", n = 19)

tmap_mode("plot")
tm_shape(yorhborough_projected) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(tosf) +
  tm_dots(col = "dbcluster",  palette = colours, style = "cat")
```

